\subsubsection {SALSA producer}
\input{producer-pseudo}
The description of SALSA producer functions is presented in Algorithm~\ref{alg:producer-non-fifo}. 
The insertion of a new task consists of two stages: 
1) finding a chunk for task insertion (if necessary), and 2) adding a task to the chunk. 

\paragraph {Finding a chunk.}
The chunk for task insertions is kept in the local producer variable \emph{chunk} (line~\ref{alg:line:chunk} in Algorithm~\ref{alg:producer-non-fifo}). 
Once a producer starts working with a chunk $c$, it continues inserting tasks to $c$ until $c$ is full. 
The producer is oblivious to chunk stealing and is not aware of its chunk moving from one pool to another. 
If the \emph{chunk}'s value is $\bot$, then the producer should open a new chunk (function \emph{getChunk}). 
In this case, the it tries to retrieve a chunk from the chunk pool and append it to the appropriate chunk list. If the chunk pool is empty then the producer either returns $\bot$ (if force$=$false), or allocates a new chunk by itself (otherwise) (lines~\ref{alg:line:no-chunk-start}--\ref{alg:line:no-chunk-end}). 

\paragraph {Inserting a task to the chunk.}
As previously described in Section~\ref{alg-structure}, different producers insert tasks to different chunks, which removes the need for synchronization among producers. 
The producer local variable \emph{prodIdx} indicates the next free slot in the chunk.
All that is left for the insertion function to do, is to put a task in that slot and to increment \emph{prodIdx} (line~\ref{alg:line:chunk-insert}).
Once the index reaches the maximal value, the \emph{chunk} variable is set to $\bot$, indicating that the next insertion operation should start a new chunk. 

\subsubsection {SALSA consumer without stealing}
\input{consumer-pseudo}
The consumer's algorithm without stealing is given in the left column of Algorithm~\ref{alg:non-fifo}.
The consumer first finds in its chunk lists a nonempty chunk if which it is the owner. it then invokes {\bf takeTask()} to retrieve a chunk from it.

We now describe the way the consumer retrieves a task from a chunk in the fast path with no stealing. 
Unlike producers, which have exclusive access to insertions in a given chunk, a consumer must take into account the possibility of stealing. 
Therefore, it should notify other processes which task it is about to take. 

To this end, each node in the chunk list keeps an index of the taken prefix of its chunk in the \emph{idx} variable, which is initiated to $-1$. 
A consumer that wants to take a task $T$, first increments the index, then checks the chunk's ownership, and finally changes the chunk entry from $T$ to a special value \emph{TAKEN} (lines~\ref{alg:lines:ind-inc}--\ref{alg:lines:fast-path}). By doing so, a consumer guarantees that \emph{idx} always points to the last taken task or to a task that is about to be taken. Hence, a process that is stealing a chunk from a node with $\textit{idx} = i$ can assume that the tasks in the range $[0 \ldots i)$ have already been taken. The logic for dealing with stolen chunks is described in the next section.



